MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-20 paper.Rmd
Move statement of need section.
Comment unneeded text.

Energy flows through society enable economic activity and facilitate human flourishing.
To understand economic growth and human well-being, 
the field of energy analysis evaluates energy flows
from the primary stage 
(coal, oil, natural gas) 
to the final stage
(energy purchased by consumers, such as refined petroleum and electricity)
and ultimately to the useful stage
(heat, mechanical drive, and light),
the last energy before energy services
(transport, thermal comfort, and illumination).
Societal exergy analysis (SEA), an extension of energy analysis,
quantifies energy flows as exergy, 
the physical work potential of energy.
Historically, SEA has analyzed energy flows through specific countries
using Excel spreadsheets, 
with data in varying and inconsistent formats 
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa].

The forces on stars, galaxies, and dark matter under external gravitational
fields lead to the dynamical evolution of structures in the universe. The orbits
of these bodies are therefore key to understanding the formation, history, and
future state of galaxies. The field of "galactic dynamics," which aims to model
the gravitating components of galaxies to study their structure and evolution,
is now well-established, commonly taught, and frequently used in astronomy.
Aside from toy problems and demonstrations, the majority of problems require
efficient numerical tools, many of which require the same base code (e.g., for
performing numerical orbit integration).

@@

>>>>

Energy flows through society enable economic activity and facilitate human flourishing.
To understand economic growth and human well-being, 
the field of energy analysis evaluates energy flows
from the primary stage 
(coal, oil, natural gas) 
to the final stage
(energy purchased by consumers, such as refined petroleum and electricity)
and ultimately to the useful stage
(heat, mechanical drive, and light),
the last energy before energy services
(transport, thermal comfort, and illumination).
Societal exergy analysis (SEA), an extension of energy analysis,
quantifies energy flows as exergy, 
the physical work potential of energy.

<!-- The forces on stars, galaxies, and dark matter under external gravitational -->
<!-- fields lead to the dynamical evolution of structures in the universe. The orbits -->
<!-- of these bodies are therefore key to understanding the formation, history, and -->
<!-- future state of galaxies. The field of "galactic dynamics," which aims to model -->
<!-- the gravitating components of galaxies to study their structure and evolution, -->
<!-- is now well-established, commonly taught, and frequently used in astronomy. -->
<!-- Aside from toy problems and demonstrations, the majority of problems require -->
<!-- efficient numerical tools, many of which require the same base code (e.g., for -->
<!-- performing numerical orbit integration). -->

@@

Historically, SEA has analyzed energy flows through specific countries
using Excel spreadsheets, 
with data in varying and inconsistent formats 
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa].
